Estimation and Implications of Bias in EPA Pollution Measurement

### 2022-01-11 paper/5min-presentation/5min-presentation.Rmd
Day's end commit: lambda and S3 documentation, lab notes, reorganizing docs.

```{r get PA sensor locations all, include=F}
result = jsonlite::fromJSON("../../data/test_data/manual_webpage_download_USmap_2021-11-29.txt")
library(zoo)
# Get start and last_seen dates from all sensors near the US
pa_data2 = as.data.frame(result$data) %>%
  purrr::set_names(result$fields) %>%
  mutate(date_start = lubridate::as_datetime(date_created),
         date_last = lubridate::as_datetime(last_seen),
         month_start = as.yearmon(date_start),
         month_last = as.yearmon(date_last)) %>%
  select(longitude, latitude, everything()) %>%
  arrange(date_start) %>%
  lonlat_country_filter(lon_col='longitude', lat_col='latitude') %>%
  filter(private == 0,  # public sensor
         location_type == 0,  # outdoor sensor
         channel_state != 0)  # has at least one PM sensor
```

>>>>

```{r get PA sensor locations all, include=F}
result = jsonlite::fromJSON("../../data/test_data/manual_webpage_download_USmap_2021-11-29.txt")
library(zoo)
# Get start and last_seen dates from all sensors near the US
pa_data2 = as.data.frame(result$data) %>%
  purrr::set_names(result$fields) %>%
  mutate(date_start = lubridate::as_datetime(date_created),
         date_last = lubridate::as_datetime(last_seen),
         month_start = as.yearmon(date_start),
         month_last = as.yearmon(date_last)) %>%
  select(longitude, latitude, everything()) %>%
  arrange(date_start) %>%
  lonlat_country_filter(lon_col='longitude', lat_col='latitude') %>%
  filter(private == 0,  # public sensor
         location_type == 0,  # outdoor sensor
         channel_state == 3)  # has 2 PM sensors (so we can QA check)

write.csv(pa_data2,
          "../../data/test_data/manual_webpage_download_USmap_2021-11-29_filtered.csv",
          row.names=F)
```
